formula1

### 2020-05-20 inst/formula1.Rmd
slight tweaks and use of better idiom

(note that the constrained maximum is on the boundary of the
admissible region with $p_\mathrm{Hamilton}\approxequal\frac{1}{25}$).

## Null of Hamilton being better than other players

@@

```{r,L4like,cache=TRUE}
small <- 0.01
L4 <- maxp(formula1, startp=c(small, rep((1-small)/24,23)),fcm=rbind(c(-1,1,rep(0,22))),fcv=0,give=TRUE)
L4
```

Calculating the support and asymptotic p-values:
```{r,l4val}
#L2 - L4$value 
#pchisq(2*(L2 - L4$value),df=1,lower.tail=FALSE)
2+3
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
loglik(indep(mHP),HP)
```

@@

```{r,profsupcalc,cache=TRUE}
p <- seq(from=0.15,to=0.25,len=10)
u <- profsupp(HP,"pole",p,n=27)
u
plot(p,u-max(u))
```

>>>>

(note that the constrained maximum is on the boundary of the
admissible region with $p_\mathrm{Hamilton}\approx\frac{1}{25}$).

## Null of Hamilton being better than all other players

@@

```{r,L4like,cache=TRUE}
samep.test(formula1,c("Hamilton","Bottas"))
```

@@

for(i in seq_len(ncol(f2017)-1)){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(y)
	names(y) <- rownames(f2017)
	HP <- HP + pwa(ordervec2supp(y),details$pole[i],"pole")
} # i loop closes
head(HP)
(mHP <- maxp(HP))
pie(mHP)
mHP <- mHP[mHP > 1e-2]
mHP
pie(mHP)
```

@@

```{r,profsupcalc,cache=TRUE}
p <- seq(from=0.15,to=0.25,len=10)
u07 <- profsupp(HP,"pole",p,n=7)
u07
plot(p,u07-max(u07))
u27 <- profsupp(HP,"pole",p,n=27)
u27
plot(p,u27-max(u27))
```
